### 2019-11-07 report/paper.tex
table

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after k-means preprocessing (originally gray-scaled, but color mapped for display purposes).}
    \label{fig:preprocessed-samples}
\end{figure}

@@

\vspace{0.5cm}

\begin{table}[h]
    \centering
    \begin{tabular}{ccc}
        \toprule
        Class name & \#samples & percentage \\
        \midrule
        waldo & 137 &  1.01\% \\
        wenda & 43&  0.32\% \\
        wizard& 27&  0.20\% \\
        negative & 13315&  98.47\% \\
        \bottomrule
    \end{tabular}
    \caption{Dataset statistics for the SVM training}
    \label{tab:dataset-stats}
\end{table}

@@

Looking at the results our classifier produced for the test images, it appears that the internal
representation of our classes is not distinctive enough to achieve a very good classification performance.
An example for a classification error that undergirds this hypothesis can be seen in Image 1 of
\autoref{fig:detections}. The dog wears glasses and its colours match the typical appearance of
Waldo but other than that they don't have much in commonn. Nevertheless, it is classified as Waldo
whereas non of the Wizards is detected successfully. Therefore we concluded that our classifier
might have picked up the most common features of Waldo like color and glasses but we did not use
enough training samples to learn enough other characteristics of Waldo so that he would stay
distinguishable from other characters in the illustrations whose appearance overlaps with his. The
same logic applies for Wenda as well. For Wizard on the other hand, we could not discover any
traits that made our algorithm detect non-Wizard characters because of a shared attribute. His
false positives appear to be random to us.

\section{Conclusion}
In this project, we useed several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& A0207441N & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after k-means preprocessing (originally gray-scaled, but color mapped for display purposes).}
    \label{fig:preprocessed-samples}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{ccc}
        \toprule
        Class name & \#samples & percentage \\
        \midrule
        waldo & 137 &  1.01\% \\
        wenda & 43&  0.32\% \\
        wizard& 27&  0.20\% \\
        negative & 13315&  98.47\% \\
        \bottomrule
    \end{tabular}
    \caption{Dataset statistics for the SVM training}
    \label{tab:dataset-stats}
\end{table}

@@

Looking at the results our classifier produced for the test images, it appears that the internal
representation of our classes is not distinctive enough to achieve a very good classification performance.
An example for a classification error that underlines this hypothesis can be seen in \( I_1 \) of
\autoref{fig:detections}. The dog wears glasses and its colours match the typical appearance of
Waldo but other than that they don't have much in common. Nevertheless, it is classified as Waldo,
whereas the Wizard is not detected. Therefore we concluded that our classifier
might have picked up the most common features of Waldo like color and glasses but we did not use
enough training samples to learn enough other characteristics of Waldo so that he would stay
distinguishable from other characters in the illustrations whose appearance overlaps with his. The
same logic applies to Wenda as well. For Wizard on the other hand, we could not discover any
traits that made our algorithm detect non-Wizard characters because of a shared attribute. His
false positives appear very much random to us.

\section{Conclusion}
In this project, we used several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& A0207441N & e0445541@u.nus.edu & HOG/HOV \& SVM, Report \\
    David Drews& Axx &e0454245@u.nus.edu & Haar Cascade, Report \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & Histogram Correlation, Report \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

\pagebreak
